\subsection{Methodology and Metrics}


	The team will be divided into two groups: the hardware team and the software team. The
	hardware team will be responsible for installing the system in the facility, developing the new
	hardware components, and the software team will be primarily responsible for developing the
	software application both in tablet and PC and a server side with a web framework that allows
	future processing of historical data. Both teams will work in the communications module of both
	sides.

	The project at hand is based on the integration of modules which contain the new features.
	(Therefore the metrics used to track progress will be based on the completion of the tasks which
	can also be divided in the same manner - Metrics)

	Hardware team tasks:
	\begin{itemize}
		\item Design and implement window motor control hardware.
		\item Implement wind speed control system (algorithm)
		\item Implement a communication interface between microcontroller and server.
		\item Perform Signal Conditioning on strain gauge signals.
		\item Design and Implement PCB.
		\item Design balance base and install it along with balance.
		\item Implement an extra sensor for side force measurement and a tunnel external barometric
			pressure sensor for additional wind speed corroboration.
		\item Install cabling, sensors and encasing for circuitry.
		\item Install Power Supply in implementation.
		\item Refine previous microcontroller’s software.
		\item Implement software library for added components.
	\end{itemize}

	Software team tasks:
	\begin{itemize}
		\item Web Server
		\begin{itemize}
			\item Database Design and Implementation for Data Storage
			\item Web Server Dashboard for Historical Data
			\item Statistical Analysis Capability
			\item REST API to access data.
			\item Coefficient Calculation (Aerodynamics related).
			\item Historical Collection of Experiments
		\end{itemize}
		\item PC application.
		\begin{itemize}
			\item Implement tablet features into PC
			\item Wind Speed Calculations
			\item Statistical Visualization of experimental data
			\item Access Control Privileges
			\item Image Capture of Models to store on Database
			\item Database Storage
		\end{itemize}
		\item Tablet Application
		\begin{itemize}
			\item Basic Experiment Management
			\item Statistical Visualization of experimental data
			\item Alternate method to capture Images
		\end{itemize}
	\end{itemize}


	FIGURE COMPONENTS